---
title: "Quickstart"
author: "Andrew Martin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
library(LearnDC)
```

Welcome to LearnDC!  This vignette walks you through some of the basic functions in the package.

## Basic structure of a call
To get data using LearnDC, first think about the _level_ (single school?  all of DC?) of the data you are looking for, then think about the _kind_ (graduation?  enrollment?) of information you want.

## The levels
LearnDC returns data at four levels of depth:

1.  **School:** individual school level data
2.  **LEA:**  data aggregated to all the schools run by school _operators_ (eg, DCPS, KIPP)
3.  **Sector:** data aggregated to all the schools by _sector_ (ie, Charter, District) 
4.  **State:** data aggregated data on all the schools in DC.  (and yes, DC is a [state](https://www.dcvote.org/))

Note that you don't specify a particular school, LEA, etc when making the call.  If you're looking for individual school data, you call `GetSchool` and then filter the response.

## Data available at each level

`GetExhibits` shows the available data for each aggregation level.
If, for instance, you wanted to know what exhibits were valid for `GetSchool`:

```{r}

GetExhibits(level = 'school')

```

## An example: Enrollment data

Let's say you were interested in getting enrollment data for all four aggregation levels.  Here's what the calls would look like:

```{r}
enr_sch <- GetSchool(exhibit = 'enrollment')
head(enr_sch)
```

```{r}
enr_lea <- GetLEA(exhibit = 'enrollment')
head(enr_lea)
```

```{r}
enr_sec <- GetSector(exhibit = 'enrollment')
head(enr_sec)
```

```{r}
enr_dc <- GetState(exhibit = 'enrollment')
head(enr_dc)
```
